Proposal: WNBA vs NBA Earnings In Comparable Players

### 2022-10-11 Proposal/Proposal.tex
Update Proposal.tex
Remove lipsum, cannot be compiled on my computer
Update Proposal.tex
Updated proposal refs
Commit
Updated Proposals with full citations

% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

\paragraph{Introduction}
I have chosen to take a close examination of WNBA and NBA players statistics and salaries. There is not a huge amount of current work on the subject, and it was difficult to find a solid enough data set of WNBA players and salaries. This is an important and engaging subject to me because I love basketball and want to see the game grow as much as possible, and hopefully with some statistical analysis of the data I can find trends into why the WNBA salaries are so exorbitantly lower than the NBA's for equivalent players.

\paragraph{Specific Aims}
I would like to compare not just salaries of WNBA vs NBA players, which is something that has been done numerous times, but to go further in depth and examine salaries vs team salary caps, league revenues, games played, and statistical performances for each player. I am interested to learn if a similarly performing player in the WNBA gets a comparable salary (adjusted for league revenue/average salaries) to an NBA player, if there are certain statistics in the NBA that result in higher adjusted salaries than the WNBA and vice versa, and similar questions.

\paragraph{Data}
I have two data sets that I have been manipulating using a python script I wrote to make them more readable. The first is a collection of WNBA players in the 2018 league season and a number of descriptive statistics, including their age, number of games played, and various basketball stats. I also amended it to include their salaries using a separate website link. The second data set is similar but for NBA players in the same season. I plan to amend both to include league average salaries and league income to be able to make league adjusted statistics.

@@

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

>>>>

% for space filling
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

\paragraph{Introduction}
I have chosen to take a close examination of WNBA and NBA players statistics and salaries. It was 
extremely difficult to find a solid enough data set of WNBA players and salaries. This is an important 
and engaging subject to me because I love basketball and want to see the game grow as much as possible, 
and hopefully with some statistical analysis of the data I can find trends into why the WNBA salaries 
are so exorbitantly lower than the NBA's for equivalent players.
\newline
There have been numerous studies surrounding that of the NBA and the WNBA and the differences in salaries.
For example, one such paper authored by Elle Baker discusses the intra-league salary distribution and
how WNBA players, despite getting paid far less, have much less "salary inequality"
\cite{baker2020comparison}. Another argues for an increase in salaries in the WNBA (a cause everyone
should be able to get behind) by citing the league's growth in fans and revenues \cite{ettienne2019s}.
There seems to be a lack of specific adjusted salary comparisons, however, and I hope to build off articles
like these to further the conversation.

\paragraph{Specific Aims}
I would like to compare not just salaries of WNBA vs NBA players, which is something that has been 
done numerous times, but to go further in depth and examine salaries vs team salary caps, league 
revenues, games played, and statistical performances for each player. I am interested to learn i
f a similarly performing player in the WNBA gets a comparable salary (adjusted for league revenue/average
salaries) to an NBA player, if there are certain statistics in the NBA that result in higher adjusted 
salaries than the WNBA and vice versa, and similar questions.
These are similar, yet more in depth questions to the ones posed by Elle Baker.

\paragraph{Data}
I have two data sets that I have been manipulating using a python script I wrote to make them more 
readable. The first is a collection of WNBA players \cite{first} in the 2018 league season and a number of 
descriptive statistics, including their age, number of games played, and various basketball 
stats. I also amended it to include their salaries using a separate website link. The second data 
set is similar but for NBA players in the same season \cite{nba}. I plan to amend both to include league average 
salaries and league income to be able to make league adjusted statistics.

@@

\bibliography{../Proposal/refs}
\bibliographystyle{chicago}
